<!--
%\VignetteIndexEntry{Introduction to the rif package}
%\VignetteEngine{knitr::rmarkdown}
%\VignetteEncoding{UTF-8}
-->

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

Introduction to the rif package
===============================

`rif` is an R wrapper for the [Neuroscience Information Framework (NIF)](https://www.neuinfo.org/)  APIs.

* API docs at <https://neuinfo.org/about/webservices>

## Install

Stable `rif` version from CRAN

```{r eval=FALSE}
install.packages("rif")
```

Or, the development version from Github

```{r eval=FALSE}
devtools::install_github("ropensci/rif")
```

```{r}
library("rif")
```

## Summary

```{r}
out <- rif_summary("cellular")
head(out$result$federationSummary$results)
```

## Query

List NIF query categories

```{r}
rif_query_categories()
```

## Vocabulary

Search for vocabulary terms

```{r}
vocabulary_search("cell", limit = 3)
```

## Lexical

Break up text into various things

```{r}
text <- "Lorem ipsum inceptos dolor nisi torquent porttitor donec, blandit scelerisque
mattis cras quis mi, aliquam sagittis. Convallis placerat commodo imperdiet varius nunc
tempus urna vitae ultrices tristique eu mi ornare velit donec, posuere laoreet pretium
vitae porta augue porta feugiat in sapien egestas. Quam odio nullam pulvinar litora
curabitur amet lacus sociosqu gravida ligula molestie dui netus fusce bibendum
scelerisque, dictum malesuada proin elit etiam aliquam, mattis euismod donec nisl facilisis."
text <- gsub("\n", "", text)
```

### Sentences

```{r}
lexical_sentences(text)
```

### Chunks

```{r}
head(lexical_chunks(text))
```

### Entities

```{r}
head(lexical_entities(text))
```

## Literature

Search

```{r}
literature_search(query = "cellular", count = 5)
```

Get retractions

```{r}
out <- literature_retractions()
out[1:20]
```

Then get info on some articles

```{r}
arts <- literature_pmid(pmid = out[1:2])
lapply(arts, "[[", "title")
```

## Data

Search for data

```{r}
out <- federation_search("cellular")
out$query
head(out$result$results)
```

Get some data

```{r}
out <- federation_data(id = "nlx_152871-2")
out$result$result
```
